Communication-efficient Learning from Multiple Experts

### 2017-10-03 draft/draft.tex
paper fix

In this paper, we propose a method for training a classification system from data labeled by multiple client annotators, where only a small subset of annotators are optimally chosen to reduce communication effort. 
We define an iterative optimization procedure where the sparsity of a client weight vector is enforced while reducing the overall classification error. Using a set of experiments, we show that our approach can pertain the classification performance as on the complete set of labelers while reducing the communication effort by over 70\% on several different tasks.

%submit  abstract until 13.04

@@

\section{Introduction}
Machine Learning systems depend on our ability to gather a large set of data. In a large number of scenarios, we gather labeled data from multiple separate sources with varying reliability and join this data into one machine learning model. Furthermore, many times we are limited in how many data sources we are allowed to use, because of budget constraints, limited processing power or insufficient communication bandwidth.

First important fitting scenario is crowdsourcing. When using crowdsourcing systems such as Amazon Mechanical Turk, we can gather labelled data from multiple annotators. After gathering this training data, we need to join the labelling decisions and train one machine learning system while leveraging all of the annotations. Relying on a concept of \textit{wisdom of crowds}, we can assume that if we gather data from a sufficient number of people, on average most of them will give correct labelling decision. However, gathering data from a large amount of annotators can be expensive, as workers on Amazon Mechanical Turk require payment for their work. There fore we would benefit from a procedure of prior determination of the expertise of the annotators. In this case, the joining process can be optimized by estimating the expertise of the annotators, selecting the most reliable ones and determining weights of their decisions.

Moreover, in a rising area of \textit{Internet of Things} (IoT)we can have similar problems. In IoT systems, a large number of sensors provide information about the environment. Communication among multiple sensors can be costly in terms of processing power. Furthermore, this communication can be done among sensors that are limited with power consumption constraints.

@@

On the other hand, there are are also multiple more theoretical frameworks. For example, Wang et al.~\cite{wang2015efficient} propose a selection of sensors based on Directed Acyclic Graphs (DAGs) in resource-constrained scenarios. However, they do not deal with annotating data, so their ideas does not completely fit to our problem.

@@

In summary, we make the following contributions:
\begin{itemize}
\item We propose a methodology for selecting an optimal subset of workers in a classification system with multiple labelers
\item We create a procedure for selecting and determine weights of labelers independent of type machine learning methods selected for modeling the annotating process
\item Using a set of experiments with real and synthetic data, we show that we can obtain accurate classification system with a learned annotator subset.
\end{itemize}

@@

In order to still use gradient descent as a convex optimization method with the $L_1$ norm, we use the method of subgradient when updating the value of $v$. The update that we derived is the following:
\begin{equation}
 v= v + S_{\lambda} (x-t_s \frac{y_n}{v}, \lambda)
\end{equation}
where
\begin{equation}
S_{\lambda} = 
\left\{
	\begin{array}{ll}
		x-\lambda  & \mbox{if } x > \lambda  \\
		x+\lambda & \mbox{if } x < -\lambda \\
		0 & \mbox{otherwise}
	\end{array}
\right.
\end{equation}

@@

>>>>

In this paper, we propose a method for training a classification system from data labeled by multiple client annotators, where only a small subset of annotators are optimally chosen to reduce communication effort. 
We define an iterative optimization procedure where the sparsity of a client weight vector is enforced while reducing the overall classification error. Using a set of experiments with real and synthetic data, we show that our approach can pertain the classification performance as on the complete set of labelers while reducing the communication effort by over 70\% on several different tasks.

@@

\section{Introduction}
Supervised machine learning depends on our ability to gather a large set of labeled data. In a large number of scenarios, we can benefit from labeled data gathered by querying multiple separate sources with varying reliability and join this data into one machine learning model. However, many times we are limited in the number of data sources that we are allowed to use, because of budget constraints, limited processing power or insufficient communication bandwidth. This causes the need for a framework that would enable resource-efficient combination of labeled data from multiple sources.

First important fitting scenario to this framework is crowdsourcing. When using crowdsourcing systems such as Amazon Mechanical Turk, we can gather labelled data from multiple annotators. After gathering this training data, we need to join the labelling decisions and train one machine learning system while leveraging all of the annotations. Relying on a concept of \textit{wisdom of crowds}, we can assume that if we gather data from a sufficient number of people, on average most of them will give correct labelling decision. However, gathering data from a large amount of annotators can be expensive, as workers on Amazon Mechanical Turk require payment for their work. Therefore we would benefit from a procedure of prior determination of the annotators' expertise. In this case, the joining process can be optimized by estimating the expertise of the annotators, selecting the optimal subset and determining weights of the annotators' labels.

Moreover, in a rising area of \textit{Internet of Things} (IoT) we can have similar problems. In IoT systems, a large number of sensors provide information about the environment. Communication among multiple sensors can be costly in terms of processing power. Furthermore, this communication can be done among sensors that are limited with power consumption constraints.

@@

On the other hand, there are are also multiple more theoretical frameworks. For example, Wang et al.~\cite{wang2015efficient} propose a selection of sensors based on Directed Acyclic Graphs (DAGs) in resource-constrained scenarios. However, they do not deal with annotating data, so their ideas do not completely fit to our problem.

@@

In summary, we make the following contributions:
\begin{itemize}
\item We propose a methodology for selecting an optimal subset of workers in a classification system with multiple labelers
\item We create a procedure for selecting and determine weights of labelers independent of type machine learning methods selected for modeling the annotating process
\item Using a set of experiments with real and synthetic data, we show that we can obtain accurate classification system with the learned annotator subset.
\end{itemize}

@@

In order to still use gradient descent as a convex optimization method with the $L_1$ norm, we use the method of subgradient when updating the value of $v$. The update that we derived is the following:
\begin{equation}
 v= v + S_{\lambda} (v-t_s \frac{\partial L}{\partial v}, \lambda)
\end{equation}
where
\begin{equation}
S_{\lambda} (k, \lambda) = 
\left\{
	\begin{array}{ll}
		k-\lambda  & \mbox{if } k > \lambda  \\
		k+\lambda & \mbox{if } k < -\lambda \\
		0 & \mbox{otherwise}
	\end{array}
\right.
\end{equation}

@@

Multiclass classification:

\begin{equation}
 L(w,v)= -\frac{1}{N} \sum_{n=1}^N \sum_{k=1}^K (\hat{y}_{nk} \log \sum_{i=1}^M v_i y_{nik}) + \psi \sum_{i=1}^{M} (y_{ni} - z_{ni})^2+\lambda \mid v \mid
\end{equation}

Full expertise model:

\begin{equation}
\begin{split}
 L(w,v)= -\frac{1}{N} \sum_{n=1}^N (\hat{y}_n \log \sum_{i=1}^M v_{ni} y_{ni} + (1-\hat{y}_n) \log(1-\sum_{i=1}^M v_{ni} y_{ni})) + \\ \psi \sum_{i=1}^{M} (y_{ni} - z_{ni})^2+\sum_{n=1}^{N}\lambda \mid v_n \mid
\end{split} 
\end{equation}
